---
title: "make plots"
output: html_document
---

Plots to make here
- A table with the error/bias numbers for all runs, should also have a ranking
- Main sims plot illustrating main point (DONE)
- All sims plot (except sampling) for appendix (DONE)
- Sampling sims plot (DONE)
- Performance plot for main text (DONE)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(xtable)
library(tidyverse)
library(cowplot)
palette = c(
  "#E69F00",
  "#56B4E9",
  "#009E73",
  "#D55E00",
  "#0072B2",
  "#CC79A7",
  "#999999",
  "#F0E442"
)
```


```{r, data}
df_sim = read_csv(
  '/Users/georgeberry/Dropbox/project-autocorr/data/new_sims.csv'
)
```

```{r, make_data}
df = df_sim %>%
  pivot_longer(
    cols=Y_no_model:Y_hat_egoalter_full,
    names_to='model',
    values_to='model_val'
  ) %>%
  mutate(
    mae=abs(model_val - Y_true) / Y_true,
    bias=(model_val - Y_true) / Y_true,
    model=case_when(
      model == 'Y_no_model' ~ 'No model',
      model == "Y_hat_node_nonetwork" ~ "Node\n(no network)",
      model == "Y_hat_node_basic" ~ "Node",
      model == "Y_hat_node_full" ~ "Node (more controls)",
      model == "Y_hat_edge_basic" ~ "Edge",
      model == "Y_hat_edge_full" ~ "Edge (more controls)",
      model == "Y_hat_egoalter_basic" ~ "Ego-alter",
      model == "Y_hat_egoalter_full" ~ "Ego-alter (more controls)",
    ),
    model=factor(
      model,
      levels=c(
        'No model',
        "Edge",
        "Edge (more controls)",
        "Node\n(no network)",
        "Node",
        "Node (more controls)",
        "Ego-alter",
        "Ego-alter (more controls)"
      )
    )
  )
```

```{r}
df %>%
  
  ggplot(aes(x=model, y=mae)) +
  geom_boxplot() +
  facet_wrap(~sampling) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```


```{r}
df %>%
  ggplot(aes(x=model, y=bias)) +
  geom_boxplot() +
  facet_wrap(~sampling) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```

  
  
```{r}  
  mutate(
    
    
    Y_no_model=abs(Y_no_model - Y_true) / Y_true,
    Y_hat_node=abs(Y_hat_node - Y_true) / Y_true,
    Y_hat_node_nonetwork=abs(Y_hat_node_nonetwork - Y_true) / Y_true,
    Y_hat_edge=abs(Y_hat_edge - Y_true) / Y_true,
    Y_hat_egoalter=abs(Y_hat_egoalter - Y_true) / Y_true,
    Y_hat_egoalter_passed=abs(Y_hat_egoalter_passed - Y_true) / Y_true,
    Y_hat_egoalter_hardmode=abs(Y_hat_egoalter_hardmode - Y_true) / Y_true,
  ) %>%
  select(
    sim,
    level,
    Y_no_model,
    Y_hat_node,
    Y_hat_node_nonetwork,
    Y_hat_edge,
    Y_hat_egoalter,
    Y_hat_egoalter_passed,
    Y_hat_egoalter_hardmode
  ) %>%
  pivot_longer(Y_no_model:Y_hat_egoalter_hardmode, names_to='model', values_to='val') %>%
  mutate(
    model=case_when(
      model == 'Y_no_model' ~ 'No model',
      model == "Y_hat_node" ~ "Node",     
      model == "Y_hat_node_nonetwork" ~ "Node\n(no network)",
      model == "Y_hat_edge" ~ "Edge",
      model == "Y_hat_egoalter" ~ "Ego-alter",
      model == "Y_hat_egoalter_passed" ~ "Ego-alter\n(augmented)",
      model == "Y_hat_egoalter_hardmode" ~ "Ego-alter\n(downsampled)"
    ),
    model=factor(model, levels=c('No model', "Node\n(no network)", "Node", "Edge", "Ego-alter", "Ego-alter\n(augmented)", "Ego-alter\n(downsampled)")),
    sim=case_when(
      sim == "indep" ~ "Independent",     
      sim == "degcorr" ~ "Degree",
      sim == "unobs" ~ "Unobserved",
      sim == "main" ~ "Main",
      sim == "weirdsamp" ~ "Sampled",
      sim == "new_graph_main" ~ "New Graph",
      sim == "new_graph_indep" ~ "New Graph (indep)",
      sim == "new_graph_equal" ~ "New Graph (equal)",
    ),
    sim=factor(sim, levels=c("Independent", "Degree", "Unobserved", "Main", "Sampled", "New Graph", "New Graph (indep)", "New Graph (equal)"))
  )

df_bias = bind_rows(
  df_main_node,
  df_main_edge,
  df_weirdsamp_node,
  df_weirdsamp_edge,
  df_indep_node,
  df_indep_edge,
  df_degcorr_node,
  df_degcorr_edge,
  df_unobs_node,
  df_unobs_edge,
  df_new_graph_main_node,
  df_new_graph_main_edge,
  df_new_graph_equal_node,
  df_new_graph_equal_edge,
  df_new_graph_indep_node,
  df_new_graph_indep_edge
) %>%
  mutate(
    Y_no_model=(Y_no_model - Y_true) / Y_true,
    Y_hat_node=(Y_hat_node - Y_true) / Y_true,
    Y_hat_node_nonetwork=(Y_hat_node_nonetwork - Y_true) / Y_true,
    Y_hat_edge=(Y_hat_edge - Y_true) / Y_true,
    Y_hat_egoalter=(Y_hat_egoalter - Y_true) / Y_true,
    Y_hat_egoalter_passed=(Y_hat_egoalter_passed - Y_true) / Y_true,
    Y_hat_egoalter_hardmode=(Y_hat_egoalter_hardmode - Y_true) / Y_true,
  ) %>%
  select(
    sim,
    level,
    Y_no_model,
    Y_hat_node,
    Y_hat_node_nonetwork,
    Y_hat_edge,
    Y_hat_egoalter,
    Y_hat_egoalter_passed,
    Y_hat_egoalter_hardmode
  ) %>%
  pivot_longer(Y_no_model:Y_hat_egoalter_hardmode, names_to='model', values_to='val') %>%
  mutate(
    model=case_when(
      model == 'Y_no_model' ~ 'No model',
      model == "Y_hat_node" ~ "Node",     
      model == "Y_hat_node_nonetwork" ~ "Node\n(no network)",
      model == "Y_hat_edge" ~ "Edge",
      model == "Y_hat_egoalter" ~ "Ego-alter",
      model == "Y_hat_egoalter_passed" ~ "Ego-alter\n(augmented)",
      model == "Y_hat_egoalter_hardmode" ~ "Ego-alter\n(downsampled)"
    ),
    model=factor(model, levels=c('No model', "Node\n(no network)", "Node", "Edge", "Ego-alter", "Ego-alter\n(augmented)", "Ego-alter\n(downsampled)")),
    sim=case_when(
      sim == "indep" ~ "Independent",     
      sim == "degcorr" ~ "Degree",
      sim == "unobs" ~ "Unobserved",
      sim == "main" ~ "Main",
      sim == "weirdsamp" ~ "Sampled",
      sim == "new_graph_main" ~ "New Graph",
      sim == "new_graph_indep" ~ "New Graph (indep)",
      sim == "new_graph_equal" ~ "New Graph (equal)",
    ),
    sim=factor(sim, levels=c("Independent", "Degree", "Unobserved", "Main", "Sampled", "New Graph", "New Graph (indep)", "New Graph (equal)"))
  )


df_perf = bind_rows(
  df_perf_edge,
  df_perf_node
)  %>%
  mutate(
    model=case_when(
      model == "node" ~ "Node",     
      model == "node_nonetwork" ~ "Node\n(no network)",
      model == "egoalter" ~ "Ego-alter",
      model == "egoalter_hardmode" ~ "Ego-alter\n(downsampled)",
    ),
    model=factor(model, levels=c("Node\n(no network)", "Node", "Ego-alter", "Ego-alter\n(downsampled)"))
  ) %>%
  pivot_longer(auc:accuracy, names_to='metric', values_to='val') %>%
  mutate(
    metric=case_when(
      metric == 'accuracy' ~ 'Accuracy',
      metric == 'auc' ~ 'AUC',
      metric == 'precision' ~ 'Precision',
      metric == 'recall' ~ 'Recall',
    ),
    metric=factor(metric, levels=c('AUC', 'Accuracy', 'Precision', 'Recall'))
  )
  
```


## Main sims plot (main text)

```{r}
p1 = df_bias %>%
  filter(sim == 'Main', model != "Ego-alter\n(downsampled)") %>%
  rename(
    Sampling=level
  ) %>%
  mutate(
    Sampling=case_when(
      Sampling == 'edge' ~ 'Edge',
      Sampling == 'node' ~ 'Node'
    )
  ) %>%
  ggplot(aes(x=model, y=val, fill=Sampling)) +
  geom_hline(yintercept=0, linetype='dotdash', alpha=0.5) +
  geom_boxplot() +
  labs(x='Model', y='Bias (percent)', title='Homophily bias') +
  guides(fill=FALSE) +
  theme_cowplot() +
  theme(
    axis.text=element_text(size=10)
  )

p2 = df_mae %>%
  filter(sim == 'Main', model != "Ego-alter\n(downsampled)") %>%
  rename(
    Sampling=level
  ) %>%
  mutate(
    Sampling=case_when(
      Sampling == 'edge' ~ 'Edge',
      Sampling == 'node' ~ 'Node'
    )
  ) %>%
  ggplot(aes(x=model, y=val, fill=Sampling)) +
  geom_hline(yintercept=0, linetype='dotdash', alpha=0.5) +
  geom_boxplot() +
  labs(x='Model', y='MAE (percent)', title='Homophily mean absolute error') +
  theme_cowplot() +
  theme(
    legend.position = c(0.7, 0.85),
    axis.text=element_text(size=10),
  )
```

```{r}
p_main = plot_grid(p1, p2, labels = c('A','B'))
```


## Perf plot (main text)


```{r,  fig.width=4, fig.height=1}
p3 = df_perf %>%
  #filter(level=='node') %>%
  group_by(model, metric, level) %>%
  summarize(
    std=sd(val) / sqrt(n()),
    val=mean(val)
  ) %>%
  inner_join(
    df_mae %>%
      filter(sim=='Main') %>%
      group_by(model, level) %>%
      summarize(
        std=sd(val) / sqrt(n()),
        val=mean(val)
      ),
    by=c('model', 'level'),
    suffix = c('_perf', '_mae')
  ) %>%
  rename(
    Model=model,
    Sampling=level
  ) %>%
  mutate(
    Sampling=case_when(
      Sampling == 'edge' ~ 'Edge',
      Sampling == 'node' ~ 'Node'
    )
  ) %>%
  ggplot(aes(x=val_perf, y=val_mae, color=Model, shape=Sampling)) +
  geom_hline(yintercept=0, linetype='dotdash') +
  geom_point(size=2, stroke=2) +
  facet_wrap(~metric, nrow=1) +
  lims(y = c(-0.03, 0.2)) +
  labs(x = element_blank(), y='MAE') +
  theme_cowplot() +
  theme(
    axis.text=element_text(size=8),
    legend.text=element_text(size=10),
    legend.position = 'bottom'
  ) +
  scale_shape_manual(values=c(1,3))
```

```{r}
p4 = df_perf %>%
  filter(model!='Ego-alter\n(downsampled)') %>%
  group_by(model, metric, level) %>%
  summarize(
    std=sd(val) / sqrt(n()),
    val=mean(val)
  ) %>%
  inner_join(
    df_bias %>%
      filter(sim=='Main') %>%
      group_by(model, level) %>%
      summarize(
        std=sd(val) / sqrt(n()),
        val=mean(val)
      ),
    by=c('model', 'level'),
    suffix = c('_perf', '_bias')
  ) %>%
  rename(
    Model=model,
    Sampling=level
  ) %>%
  mutate(
    Sampling=case_when(
      Sampling == 'edge' ~ 'Edge',
      Sampling == 'node' ~ 'Node'
    )
  ) %>%
  ggplot(aes(x=val_perf, y=val_bias, color=Model, shape=Sampling)) +
  geom_hline(yintercept=0, linetype='dotdash') +
  geom_point(size=4, stroke=1.5) +
  facet_wrap(~metric, nrow=1, strip.position ='bottom') +
  lims(y = c(-0.2, 0.05), x=c(0.71, 0.87)) +
  labs(x = element_blank(), y='Homophily bias\n(percent)', title='Homophily bias compared to node-level performance') +
  theme_cowplot() +
  panel_border() +
  theme(
    axis.text=element_text(size=8),
    # strip.text.x = element_blank(),
  ) +
  scale_color_manual(values=palette) +
  scale_shape_manual(values=c(1,3))
  # guides(shape=FALSE, color=FALSE)
```


 


## All sims(appendix)


```{r}
p5 = df_bias %>%
  filter(model != "Ego-alter\n(downsampled)") %>%
  mutate(
    val=ifelse(abs(val) > 0.4, sign(val) * 0.4, val)
  ) %>%
  group_by(sim, level, model) %>%
  summarize(
    std=sd(val),
    val=mean(val)
  ) %>%
  ungroup() %>%
  mutate(
    level=case_when(
      level=='edge' ~ 'Edge sample',
      level=='node' ~ 'Node sample'
    )
  ) %>%
  rename(
    Simulation=sim
  ) %>%
  ggplot(aes(x=model, y=val, color=Simulation)) +
  geom_hline(yintercept=0, alpha=0.5, linetype='dotdash') +
  #geom_boxplot() +
  geom_point(position=position_dodge(width=0.6)) +
  geom_errorbar(
    aes(ymin=val - std, ymax = val + std),
    position=position_dodge(width=0.6),
    width=0.0
  ) +
  guides(colour = guide_legend(reverse=T)) +
  scale_color_manual(values=palette) +
  labs(
    x='Model',
    y='Bias (percent)',
    title='Comparison of all models across five simulations') + 
  theme_cowplot() +
  theme(
    legend.position="top",
    axis.text=element_text(size=10)
  ) +
  coord_flip() +
  panel_border() +
  facet_wrap(~level)

p6 = df_mae %>%
  filter(model != "Ego-alter\n(downsampled)") %>%
  mutate(
    val=ifelse(abs(val) > 0.4, sign(val) * 0.4, val)
  ) %>%
  #group_by(sim, level, model) %>%
  #summarize(
  #  std=sd(val),
  #  val=mean(val)
  #) %>%
  #ungroup() %>%
  mutate(
    level=case_when(
      level=='edge' ~ 'Edge sample',
      level=='node' ~ 'Node sample'
    )
  ) %>%
  rename(
    Simulation=sim
  ) %>%
  ggplot(aes(x=model, y=val, color=Simulation)) +
  geom_hline(yintercept=0, alpha=0.5, linetype='dotdash') +
  #geom_violin() +
  geom_boxplot() +
  #geom_point(position=position_dodge(width=0.6)) +
  #geom_errorbar(
  #  aes(ymin=val - std, ymax = val + std),
  #  position=position_dodge(width=0.6),
  #  width=0.0
  #) +
  guides(colour = guide_legend(reverse=T)) +
  scale_color_manual(values=palette) +
  labs(x='Model', y='Mean absolute error (percent)') + 
  theme_cowplot() +
  coord_flip() +
  theme(
    legend.position = 'none',
    axis.text=element_text(size=10)
  ) +
  panel_border() +
  facet_wrap(~level)
```



```{r}
plot_grid(p5, p6, ncol=1, rel_heights=c(1.15,1), labels=c('A', 'B'))
```

#### MAKE A TABLE FOR THE CURIOUS

sim/level on the y axis, model on the x axis

```{r}
df_table_mae = df_mae %>%
  group_by(sim, level, model) %>% 
  summarize(std=sd(val) / sqrt(n()), mu=mean(val)) %>%
  #pivot_longer(std:mu, names_to='metric', values_to='val') %>%
  #pivot_wider(names_from=model, values_from='val') %>%
  pivot_longer(mu, names_to='metric', values_to='val') %>%
  pivot_wider(id_cols=sim:level, names_from=model, values_from='val') %>%
  arrange(level, sim) %>%
  select(level, sim, everything()) %>%
  ungroup() %>%
  mutate(
    level=case_when(
      level == 'edge' ~ 'Edge',
      level == 'node' ~ 'Node'
    )
  ) %>%
  rename(
    Sim=sim,
    `\thead{Sampling level}`=level,
    `\thead{Node (no network)}`=`Node\n(no network)`,
    `\thead{Ego-alter (augmented)}`=`Ego-alter\n(augmented)`
  )

print(
  xtable(
    df_table_mae,
    digits=3,
    caption='Mean absolute error by simulation'
  ),
  include.rownames=FALSE
)
```



```{r}
df_table_bias = df_bias %>%
  group_by(sim, level, model) %>% 
  summarize(std=sd(val) / sqrt(n()), mu=mean(val)) %>%
  #pivot_longer(std:mu, names_to='metric', values_to='val') %>%
  #pivot_wider(names_from=model, values_from='val') %>%
  pivot_longer(mu, names_to='metric', values_to='val') %>%
  pivot_wider(id_cols=sim:level, names_from=model, values_from='val') %>%
  arrange(level, sim) %>%
  select(level, sim, everything()) %>%
  ungroup() %>%
  mutate(
    level=case_when(
      level == 'edge' ~ 'Edge',
      level == 'node' ~ 'Node'
    )
  ) %>%
  rename(
    Sim=sim,
    `\thead{Sampling level}`=level,
    `\thead{Node (no network)}`=`Node\n(no network)`,
    `\thead{Ego-alter (augmented)}`=`Ego-alter\n(augmented)`
  )

print(
  xtable(
    df_table_bias,
    digits=3,
    caption='Bias by simulation'
  ),
  include.rownames=FALSE
)
```