## A minimal example

Example of one full loop of the process, good for developing or understanding

```{r setup, include=FALSE}
library(tidyverse)
library(ggraph)
library(tidygraph)
library(foreach)
library(doParallel)
library(pROC)
library(caret)
source("/Users/georgeberry/Dropbox/project-autocorr/autocorr/sim_code.R")

registerDoParallel(cores=12)
N_SIMS = 100
N_NODES = 4000
GROUND_TRUTH_LABELING_BUDGET = 500
ALPHA = 0.8  # powerlaw exponent
BETA = 0.7  # strength of homophily
EDGES_PER_NEW_NODE = 5
MAJORITY_GROUP_FRAC = 0.7
```


## new graph checks

#### check edgesamp

```{r}
g = play_bidir_powerlaw_homophily_graph(
  N_NODES,
  EDGES_PER_NEW_NODE,
  MAJORITY_GROUP_FRAC,
  0.8,
  0.7
)
g = fn_edgesamp(g)
df_nodes = g %>% activate(nodes) %>% as_tibble()
df_edges = g %>% activate(edges) %>% as_tibble()
```

40k nodes, the average GT nodde should be around 20k

```{r}
df_edges %>%
  ungroup() %>%
  mutate(rand_num=1:n()) %>%
  select(gt, rand_num) %>%
  summarize(sum(as.integer(gt) * rand_num) / sum(gt))
```

no multi-edges

```{r}
max(df_edges %>% group_by(from, to) %>% tally() %>% pull(n))
```

no self loops

```{r}
nrow(df_edges %>% filter(from == to))
```

check on the gt nodes at the edge and node levels to make sure they match

```{r}
length(unique(c(df_edges %>%
  filter(gt == 1) %>%
  pull(name_nbr), df_edges %>%
  filter(gt == 1) %>%
  pull(name_ego))))
```

```{r}
length(unique(df_nodes %>%
  filter(gt == 1) %>%
  pull(name)))
```


```{r}
setdiff(
  unique(c(df_edges %>%
  filter(gt == 1) %>%
  pull(name_nbr), df_edges %>%
  filter(gt == 1) %>%
  pull(name_ego))),
  df_nodes %>%
  filter(gt == 1) %>%
  pull(name)
)
```


#### check nodesamp

```{r}
g = play_bidir_powerlaw_homophily_graph(
  N_NODES,
  EDGES_PER_NEW_NODE,
  MAJORITY_GROUP_FRAC,
  0.8,
  1.2
)
g = fn_nodesamp(g)
df_nodes = g %>% activate(nodes) %>% as_tibble()
df_edges = g %>% activate(edges) %>% as_tibble()
```

should be about 2k

```{r}
df_nodes %>%
  mutate(rand_num=1:n()) %>%
  summarize(sum(rand_num * gt) / sum(gt))
```

```{r}
length(unique(c(df_edges %>%
  filter(gt_ego == 1) %>%
  pull(name_ego), df_edges %>%
  filter(gt_nbr == 1) %>%
  pull(name_nbr))))
```

```{r}
length(unique(df_nodes %>%
  filter(gt == 1) %>%
  pull(name)))
```

```{r}
setdiff(
  unique(c(df_edges %>%
  filter(gt_ego == 1) %>%
  pull(name_ego), df_edges %>%
  filter(gt_nbr == 1) %>%
  pull(name_nbr))),
  df_nodes %>%
  filter(gt == 1) %>%
  pull(name)
)
```


#### check degsamp

```{r}
g_orig = play_bidir_powerlaw_homophily_graph(
  N_NODES,
  EDGES_PER_NEW_NODE,
  MAJORITY_GROUP_FRAC,
  0.8,
  1.2
)
g = fn_degsamp(g_orig)
df_nodes = g %>% activate(nodes) %>% as_tibble()
df_edges = g %>% activate(edges) %>% as_tibble()
```

```{r}
length(unique(c(df_edges %>%
  filter(gt_ego == 1) %>%
  pull(name_ego), df_edges %>%
  filter(gt_nbr == 1) %>%
  pull(name_nbr))))
```

```{r}
length(unique(df_nodes %>%
  filter(gt == 1) %>%
  pull(name)))
```

```{r}
setdiff(
  unique(c(df_edges %>%
  filter(gt_ego == 1) %>%
  pull(name_ego), df_edges %>%
  filter(gt_nbr == 1) %>%
  pull(name_nbr))),
  df_nodes %>%
  filter(gt == 1) %>%
  pull(name)
)
```



```{r}
df_nodes %>%
  mutate(outdeg_rank=cut(rank(outdeg), 10, include.lowest=T)) %>%
  select(outdeg_rank, gt, outdeg) %>%
  group_by(outdeg_rank) %>%
  summarize(gt_prob=mean(gt), n=n(), outdeg=mean(outdeg)) %>%
  arrange(outdeg)

```
the rank 5 sampling prob should be n_desired_nodes * 5/deg

```{r}
GROUND_TRUTH_LABELING_BUDGET * 5 / sum(df_nodes$outdeg)
```

remember we're sampling w/o replacement in the original, 

#### classic log log plot

ain't bad!

```{r}
g %>%
  activate(nodes) %>%
  as_tibble() %>%
  mutate(outdeg=outdeg + 0.001 * rnorm(n())) %>%
  ggplot(aes(x=log(rank(-outdeg)), y=log(outdeg))) +
  geom_point()
```

plot a small graph

```{r}
g = play_bidir_powerlaw_homophily_graph(
  100,
  2,
  0.5,
  1.0,
  beta=2.0,
  gamma=0
) %>%
  activate(edges) %>%
  mutate(
    Y_ego = .N()$Y[from],
    Y_nbr = .N()$Y[to],
    Y_cat = as.integer(Y_ego == Y_nbr)
  )
```


```{r}
ggraph(g, layout='kk') +
  geom_edge_link() + # aes(color=factor(Y_cat))) +.
  geom_node_point(aes(color=factor(Y)))
```

```{r}
ggraph(g, layout='kk') +
  geom_edge_link() +
  geom_node_point(aes(color=factor(Y)))
```


### random graph gen test

```{r}
n_nodes = 10
majority_group_frac = 0.7
edges_per_node = 1
alpha = 0.8
beta = 0.7

majority_N = round(n_nodes * majority_group_frac)
majority_Y = rep(1, majority_N)
majority_X = rnorm(majority_N, 1, 1)

minority_N = round(n_nodes * (1 - majority_group_frac))
minority_Y = rep(0, minority_N)
minority_X = rnorm(minority_N, -1, 1)

# Group
Y = c(majority_Y, minority_Y)
X = c(majority_X, minority_X)

nodes = 1:n_nodes  # this gives unique ids for each node

node_df = data.frame(
    Y=Y,
    X=X
)

# Degree
D = list()
for (node in nodes) {
    D[[node]] = 0
}

# seed nodes are chose at random and completely connected (clique)
# b/c of bidir we do 2 * edges_per_node + 1
seeds = sample(nodes, 2 * edges_per_node + 1, replace=FALSE)

for (seed in seeds) {
    D[[seed]] = edges_per_node
}

edge_df = expand.grid(seeds, seeds)
colnames(edge_df) = c('from', 'to')
# filter out self loops
edge_df = edge_df %>%
  filter(from != to)

node_iter_order = sample(
  setdiff(nodes, seeds),
  length(setdiff(nodes, seeds)),
  replace=FALSE
)

for (node in node_iter_order) {
    node_grp = Y[node]
    same_grp_nodes = as.integer(Y == node_grp)
    for (edge_to_add in 1:edges_per_node) {
        # Determining a connection is a function of
        # degree, group_Y, Z

        # Using the conditional logit expression in Overgoor et al 2020
        deg_probs = exp(
          alpha * log(unlist(D) + 0.001) +
          beta * same_grp_nodes
        )
        probs = deg_probs / sum(deg_probs)

        draw = sample(
          nodes,
          1,
          replace=FALSE,
          prob=probs
        )
        #  no self-loops; no multi-edges
        while (
          (draw == node) | 
          (nrow(edge_df %>% filter(from == node, to == draw)) >= 1)
        ) {
            draw = sample(nodes, 1, replace=FALSE, prob=probs)
        }

        edge_df = bind_rows(
            edge_df,
            data.frame(from=c(node, draw), to=c(draw, node))
        )
        D[[node]] = D[[node]] + 1
        D[[draw]] = D[[draw]] + 1
    }
}
tmp = as_tbl_graph(edge_df)  %>%
  activate(nodes) %>%
  mutate(
      Y=Y[as.integer(name)],
      X=X[as.integer(name)]
  )
```

```{r}
tmp %>%
  activate(edges) %>%
  mutate(
    X_ego = .N()$X[from]
  )
```






### Testing implications of sampling proportional to node degree

```{r}
df_nodes %>%
  select(name, outdeg) %>%
  mutate(
    pr=outdeg/sum(outdeg),
  ) -> tmp

samp = sample(tmp$name, 1000, replace=FALSE, prob=tmp$pr)

df_edges %>%
  mutate(
    idx=1:n()
  ) %>%
  filter(
    from %in% samp
  ) %>%
  summarize(mean(idx))
```


### Example output data

```{r}
df = read_csv(
  '/Users/georgeberry/Dropbox/project-autocorr/data/new_graph_main_nodesamp.csv'
)
```

```{r}
df %>% summarize_all(mean)
```

### homophily calc

```{r}
  tmp = df_edges %>%
    filter(Y_ego == 1) %>%
    group_by(Y_ego, Y_nbr) %>%
    tally()
  ingroup_links = tmp %>% filter(Y_ego == 1, Y_nbr == 1) %>% pull(n)
  crossgroup_links = tmp %>% filter(Y_ego == 1, Y_nbr == 0) %>% pull(n)
  # divide the ingroup links by 2 to avoid double counting
  actual = ingroup_links / (ingroup_links + crossgroup_links)
  (actual - MAJORITY_GROUP_FRAC) / (1 - MAJORITY_GROUP_FRAC)
```

```{r}
  tmp = df_edges %>%
    filter(Y_ego == 0) %>%
    group_by(Y_ego, Y_nbr) %>%
    tally()
  ingroup_links = tmp %>% filter(Y_ego == 0, Y_nbr == 0) %>% pull(n)
  crossgroup_links = tmp %>% filter(Y_ego == 0, Y_nbr == 1) %>% pull(n)
  actual = ingroup_links / (ingroup_links + crossgroup_links)
  (actual - 0.3) / (1 - 0.3)
```

